### 2010-12-06 report/report.tex
minor
related work

\edit{Actually write this...}

@@

We evaluated the efficacy of a set of parameters by sending these
parameters to the robot and instructing it to walk for a certain length
of time. The robot always begins from the same position and returns to the
starting position at the end of the run in order to allow for uniformity
in measuring. More efficient parameters resulted in a faster gait, which
translated into a longer distance walked and a better score. After completing
an evluation, the robot sent the resulting distance walked back to the
host computer and prepared itself for a new set of parameters to evaluate.

>>>>

Various maching learning techniques have proven to be useful in finding
control policies for a wide variety of robots. Kohl and Stone\cite{1}
presented a policy gradient reinforcement learning approach for generating
a fast walk on legged robots. We experimented with this method to create
a walk for our robot (Policy Gradient Descent). Chernova and Velosa\cite{3}
took an evolutionary approach to this problem which we did not implement.
Zykov, Bongard, and Lipson\cite{4} describe the evolution of dynamic gaits 
on a physical robot requiring no prior
assumptions about the locomotion pattern beyond the fact that it should be
rhythmic.

@@

We evaluated the efficacy of a set of parameters by sending these
parameters to the robot and instructing it to walk for a certain length
of time. The robot always begins from the same position and returns to the
starting position at the end of the run in order to allow for uniformity
in measuring. More efficient parameters resulted in a faster gait, which
translated into a longer distance walked and a better score. After completing
an evaluation, the robot sent the resulting distance walked back to the
host computer and prepared itself for a new set of parameters to evaluate.
